\documentclass[11pt]{article}

\usepackage[T1]{fontenc}
\usepackage{inter} 
\renewcommand*\familydefault{\sfdefault}

\usepackage{geometry}
\geometry{
    a4paper,
    top=1.5cm,
    bottom=1.5cm,
    left=2.5cm,
    right=2.5cm
}

\setcounter{secnumdepth}{0} % remove section numbering
\pdfgentounicode=1 % make ATS friendly

\usepackage{enumitem}
\setlist[itemize]{
    noitemsep,
    left=2em
}
\setlist[description]{itemsep=0pt}
\setlist[enumerate]{align=left}
\usepackage[dvipsnames]{xcolor}
\usepackage{marvosym}
\colorlet{icnclr}{gray}
\usepackage{titlesec}
\titlespacing{\subsection}{0pt}{*0}{*0}
\titlespacing{\subsubsection}{0pt}{*0}{*0}
\titleformat{\section}{\color{Sepia}\large\fontseries{black}\selectfont\uppercase}{}{}{\ruleafter}[\global\RemVStrue]
\titleformat{\subsection}{\fontseries{bold}\selectfont}{}{}{\rvs}
\titleformat{\subsubsection}{\color{gray}\fontseries{bold}\selectfont}{}{}{}

\usepackage{xhfill} 
\newcommand\ruleafter[1]{#1~\xrfill[.5ex]{1pt}[gray]} % add rule after title in .5 x-height 

\newif\ifRemVS % remove vspace between \section & \subsection
\newcommand{\rvs}{
    \ifRemVS
        \vspace{-1.5ex}
    \fi
    \global\RemVSfalse
}

\usepackage{fontawesome5} % For FontAwesome icons

\usepackage[bookmarks=false]{hyperref} % [imp!]
\hypersetup{ 
    colorlinks=true,
    urlcolor=Sepia,
    pdftitle={My Resume},
}

\usepackage[page]{totalcount}
\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}	
\fancyhf{}							

\usepackage{amsmath}
\usepackage{amsfonts}

\begin{document}


%== HEADER ==%
\begin{center}      
    {\fontsize{24}{24}\selectfont Santhosh Raj K} \\[10pt] % Adjusted space here

    {\color{icnclr}\faMapMarker} Chennai, India \quad 
    {\color{icnclr}\faEnvelope[regular]} \href{mailto:santhoshrajk1812@gmail.com}{santhoshrajk1812@gmail.com} \quad
    {\color{icnclr}\faGithub[regular]} \href{https://github.com/sandyddeveloper}{github.com/sandyddeveloper} \quad \\[10pt]
    {\color{icnclr}\faLinkedin[regular]} \href{https://linkedin.com/in/santhoshrajk}{linkedin.com/in/santhoshrajk} \quad
    {\color{icnclr}\Mobilefone} \href{tel:+91 9345693386}{+91 9345693386}
\end{center}
%==============

\section{About Me}
Highly motivated full-stack developer with a strong foundation in Core and Advanced Python, Django, and MySQL.
Passionate about applying problem-solving abilities and technical expertise to build scalable, efficient, and high-quality solutions.
Eager to contribute as a Python Developer and grow in a dynamic team environment.
\section{Education}
\subsection{Bachelor of Computer Application \hfill \normalfont 2024}  
\subsubsection{AGURCHAND MANMULL JAIN COLLEGE, Chennai, India}
\begin{itemize}
    \item \textbf{GPA}: 8.05/10
\end{itemize}

\subsection{HSC \hfill \normalfont 2021}  
\subsubsection{ST. JOHN'S MATRICULATION HR SCHOOL, Chennai, India}
\begin{itemize}
    \item \textbf{Percentage}: 75\%
\end{itemize}

\subsection{SSLC \hfill \normalfont 2019}  
\subsubsection{ST. JOHN'S MATRICULATION HR SCHOOL, Chennai, India}
\begin{itemize}
    \item \textbf{Percentage}: 70\%
\end{itemize}

\section{Internships}
\subsection{Shiash Info Solutions (3 Months)}
\begin{itemize}
    \item Developed web applications using Python and Django.
    \item Optimized database queries for performance.
\end{itemize}

\section{Projects}
\subsection{Aluminium Pro.} 
\begin{itemize}
    \item Integrated predictive models for efficient aluminum manufacturing. 
    \item \textbf{Live link}: \href{https://aluminium-pro.onrender.com/}{aluminium-pro.onrender.com}
\end{itemize}
\subsection{Portfolio Website} 
\begin{itemize}
    \item Developed a portfolio site with smooth transitions.
    \item \textbf{Live link}: \href{https://santhoshdev-seven.vercel.app/}{santhoshdev-seven.vercel.app}
\end{itemize}

\section{Skills}
\begin{itemize}
    \item \textbf{Languages}: Python, HTML, CSS, JavaScript
    \item \textbf{Frameworks}: Django, React, Next.js
    \item \textbf{Databases}: MySQL
    \item \textbf{Tools}: Git, Canva, VS code and  Basic in Figma
\end{itemize}

\section{Achievements}
\begin{itemize}
    \item[\faCertificate] \textbf{Department Topper (2021-2024)} - Ranked 1st for 2 years
    \item[\faTrophy] \textbf{Intra-College Fest (BIT-SYNC) (2024)} - Awarded for organizing events
\end{itemize}


\section{Extracurricular Activities}
\begin{itemize}
    \item Organized and participated in technical events (BITSYNC) with 450+ participants.
    \item Placement Student Coordinator and volunteer for college events.
\end{itemize}

\end{document}
