\documentclass[11pt]{article}

\usepackage[T1]{fontenc}
\usepackage{inter} 
\renewcommand*\familydefault{\sfdefault}

\usepackage{geometry}
\geometry{
    a4paper,
    top=1.8cm,
    bottom=1in,
    left=2.5cm,
    right=2.5cm
}

\setcounter{secnumdepth}{0} % remove section numbering
\pdfgentounicode=1 % make ATS friendly

\usepackage{enumitem}
\setlist[itemize]{
    noitemsep,
    left=2em
}
\setlist[description]{itemsep=0pt}
\setlist[enumerate]{align=left}
\usepackage[dvipsnames]{xcolor}
\usepackage{marvosym}
\colorlet{icnclr}{gray}
\usepackage{titlesec}
\titlespacing{\subsection}{0pt}{*0}{*0}
\titlespacing{\subsubsection}{0pt}{*0}{*0}
\titleformat{\section}{\color{Sepia}\large\fontseries{black}\selectfont\uppercase}{}{}{\ruleafter}[\global\RemVStrue]
\titleformat{\subsection}{\fontseries{bold}\selectfont}{}{}{\rvs}
\titleformat{\subsubsection}{\color{gray}\fontseries{bold}\selectfont}{}{}{}

\usepackage{xhfill} 
\newcommand\ruleafter[1]{#1~\xrfill[.5ex]{1pt}[gray]} % add rule after title in .5 x-height 

\newif\ifRemVS % remove vspace between \section & \subsection
\newcommand{\rvs}{
    \ifRemVS
        \vspace{-1.5ex}
    \fi
    \global\RemVSfalse
}

\usepackage{fontawesome5} % For FontAwesome icons

\usepackage[bookmarks=false]{hyperref} % [imp!]
\hypersetup{ 
    colorlinks=true,
    urlcolor=Sepia,
    pdftitle={My Resume},
}

\usepackage[page]{totalcount}
\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}	
\fancyhf{}							

\usepackage{amsmath}
\usepackage{amsfonts}

\begin{document}

%== HEADER ==%
\begin{center}      
    {\fontsize{30}{30}\selectfont Santhosh Raj K} \\ \bigskip

    {\color{icnclr}\faMapMarker} Chennai, India \quad 
    {\color{icnclr}\faEnvelope[regular]} \href{mailto:santhoshrajk1812@gmail.com}{santhoshrajk1812@gmail.com} \quad
    {\color{icnclr}\Mobilefone} \href{tel:+91 9345693386}{+91 9345693386} 
    % Optional: LinkedIn or website address
    % {\color{icnclr}\faLinkedinIn} \href{https://www.linkedin.com/in/santhosh-raj-k-622179316}{santhosh raj k}
\end{center}
%==============

\section{About Me}
A highly motivated full-stack developer with a solid background in Python, Django, and React. Passionate about leveraging problem-solving skills and technical expertise to deliver high-quality solutions. I aim to contribute to impactful projects while continuously improving my knowledge in software development.

\section{Education}
\subsection{Bachelor of Computer Application \hfill \normalfont 2024}  
\subsubsection{AGURCHAND MANMULL JAIN COLLEGE, Meenambakkam, Chennai, India}
\begin{itemize}
    \item \textbf{GPA}: 8.05/10
    \item \textbf{Relevant Coursework}: 
    \begin{itemize}
        \item Data Structures
        \item Database Systems
        \item Computer Networks
    \end{itemize}
\end{itemize}

\subsection{HSC \hfill \normalfont 2021}  
\subsubsection{ST. JOHN'S MATRICULATION HR SCHOOL, Chennai, India}
\begin{itemize}
    \item \textbf{Percentage}: 75\%
    \item \textbf{Major Coursework}: 
    \begin{itemize}
        \item Computer Science
        \item Mathematics
        \item Physics and Chemistry
    \end{itemize}
\end{itemize}

\subsection{SSLC \hfill \normalfont 2019}  
\subsubsection{ST. JOHN'S MATRICULATION HR SCHOOL, Chennai, India}
\begin{itemize}
    \item \textbf{Percentage}: 70\%
\end{itemize}

\section{Internships}
\subsection{Shiash Info Solutions Private Limited (3 Months)} 
\begin{itemize}
    \item Developed full-stack web applications using Python and Django.
    \item Integrated REST APIs and worked on front-end interfaces using HTML, CSS, and JavaScript.
    \item Enhanced application performance by optimizing database queries.
\end{itemize}

\section{Projects}
\subsection{Aluminium Pro.} 
\begin{itemize}
    \item Integrated predictive models to optimize material use, reduce costs, and boost efficiency in aluminum manufacturing.
    \item Enhanced operational workflows by embedding real-time analytics for faster, data-driven decisions.
    \item Implemented scrap management strategies to minimize waste and improve sustainability.
    \item Developed user-friendly dashboards for real-time monitoring and actionable insights.
    \item \textbf{Live link}: \href{https://aluminium-pro.onrender.com/}{aluminium-pro.onrender.com/}
    \item \textbf{GitHub}: \href{https://github.com/sandyddeveloper/AluminiumPro}{https://github.com/sandyddeveloper/AluminiumPro}
\end{itemize}
\subsection{Portfolio Website} 
\begin{itemize}
    \item Built a responsive portfolio website using Next.js, showcasing my projects, skills, and experience.
    \item Integrated smooth transitions and animations for a polished user experience.
    \item \textbf{Live link}: \href{https://santhoshdev-seven.vercel.app/}{santhoshdev-seven.vercel.app}
    \item \textbf{GitHub}: \href{https://github.com/sandyddeveloper/portfolio}{https://github.com/sandyddeveloper/portfolio}
\end{itemize}

\subsection{Ecommerce Web Application - Trendify}
\begin{itemize}
    \item Developed a comprehensive eCommerce platform using Django and PostgreSQL.
    \item Implemented features like user authentication, product management, and payment gateway integration.
    \item Optimized authentication modules using threading, improving efficiency by 20\%.
    \item \textbf{GitHub}: \href{https://github.com/sandyddeveloper/Ecommerce-django.git}{https://github.com/sandyddeveloper/Ecommerce-django.git}
\end{itemize}

\section{Skills}
\subsection{Programming Languages}
\begin{itemize}
    \item Python
    \item HTML, CSS, JavaScript
\end{itemize}

\subsection{Frameworks \& Libraries}
\begin{itemize}
    \item Django
    \item React
    \item Next.js
\end{itemize}

\subsection{Databases}
\begin{itemize}
    \item PostgreSQL
    \item MySQL
    \item MongoDB
\end{itemize}

\subsection{Tools}
\begin{itemize}
    \item Git, GitHub
    \item Canva, Basic in Figma
\end{itemize}

\section{Achievements}
\begin{itemize}
    \item[\faCertificate] \textbf{Department Topper (2021-2024)} - Being ranked 1st for 2 consecutive years
    \item[\faTrophy] \textbf{Intra-College Fest (BIT-SYNC) (2024)} - Awarded for excellence as an active event organizer.
    % \item[\faCheck] Completed \textbf{INFOYSYS SPRINGBOARD }, \textbf{Info Sys} certification courses.
\end{itemize}
\section{Certifications}
\begin{itemize}
    \item GTT - Barclays Training - Life-Skills Program 11th August 2023
    \item INFOSYS Springboard Certificates
\end{itemize}
\section{Extracurricular Activities}
\begin{itemize}
    \item Organized and participated in multiple college-level technical events (BITSYNC) with over 450 participants.
    \item Served as Placement Student Coordinator.
    \item Volunteered in social awareness programs organized by the college.
    \item Actively participated in various college events as a volunteer.
\end{itemize}



\end{document}
